Vulnerability Analysis of Container Images in Neuroimaging

### 2020-08-06 paper.tex
worked on Mathieu's comments

If vulnerabilities exist in the container images, then our first approach
is to update these images in order to see the effects of such updates
on the vulnerabilities.
Updating an image involves updating all software packages that are
inside that image. We use a 
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{bash script} 
to update all images. That script checks the
package manager, which is present inside the image, and updates the image
accordingly. However, this action affects the reproducibility
of that image. For example, if a package is used in an experiment
and later that package is updated, subsequent instances of the experiment may actually
get different results.
\vspace*{-2mm}
\subsection{Image Minimization Process}

We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, an open-source tool that
helps scientists to make their research reproducible. This tool traces operating system calls used by the
application during execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree of a particular package.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

@@

\change{Our experiments concluded considerable discrepancies in the results obtained by
these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
While comparing scanner results, we exluded two images \texttt{bids/antscorticalthickness:v2.2.0-1} and
\texttt{bids/antscorticalthickness:v2.2.0-1} because Vuls
cannot scan these image, hence no results are present to compare.
%The reason behind excluding
%vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
%to report pending patches that need to be applied to specific packages,
%whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
%vulnerabilities in packages. We exluded other two images because Vuls
%can not scan these image, hence no results are present to compare.
In most cases,
Anchore reports more vulnerabilities than Vuls and Clair resulting in 
the Jaccard coefficient of 0.63 with Clair, 0.59 with Vuls,
whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.86.
Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners in Docker images and the overlap between them.
This Figure also excludes two non-comparable images, which cannot be scanned with Vuls.
It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 699 by Clair, and 536 by Vuls.}
\newline\\
As the number and type of vulnerabilities reported by the these scanners are significantly different from each other,
we desire to investigate the reasons behind these differences.
Following our investigation, we are able to explain some of the reasons behind
the differences. 
Such reasons were resulted from the way these scanners function or behave 
in particular, the following actions by the scanners are indicative:
\begin{itemize}
   \item scanners ignoring vulnerabilities in Linux-kernel-header packages,
   \item scanners referring to different vulnerability databases,
   \item different frequency of updating their databases,
   \item bugs in scanners. 
\end{itemize}

@@

Our second approach involves the deletion of unnecessary packages from the images.
We tested our approach on 5 different images covering the spectrum of Figure~\ref{fig:graph1}. We find that
after the size reduction process, sometimes the scanning results deviate only a little from the results
without minimization. While the minimization process results in significant reduction
in the number of vulnerabilities in some cases, we find that in other cases the effect
is negligible. In other words, the image reduction was inconsistent.
According to our analysis, this can be due to two reasons: \rom{1}) the number of
deleted packages
and \rom{2}) the kind of deleted packages. 
For an instance, if the deletion is for a package that includes a lot of vulnerabilities,
that particular deletion naturally results in the drop of number of vulnerabilities.
In other
words, deleting more packages reduces more vulnerabilities. 
For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.

>>>>

If vulnerabilities exist in the container images, then our first approach
is to update these images in order to see the effects of such updates
on the vulnerabilities.
Updating an image involves updating all software packages that are
inside that image. We use a 
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{bash script} 
to update all images. That script checks which
package manager is present inside the image, and based on that
it updates OS packages of the image
accordingly. However, this action affects the reproducibility
of that image. For example, if a package is used in an experiment
and later that package is updated, subsequent instances of the experiment may actually
get different results.
\vspace*{-2mm}
\subsection{Image Minimization Process}

%We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
%An interesting choice to do so would be to use 
%Neurodocker~\cite{neurodocker}.
%This tool traces and deletes unnecessary files.
%However, it does not affect the number of installed packages.
%Since image scanners report vulnerabilities according to the installed
%packages. Therefore, after
%minimization the same number of vulnerabilities is still reported.
%Consequently, we need to reduce the number of installed packages
%in the images by deleting unnecessary packages. For that, it is required to figure
%out which packages we need for the pipeline to function properly.
\change{We revert to our second approach i.e. image minimization to reduce the number of vulnerabilities in the
images with the aim to remove unused packages from the images.
We use Neurodocker for this purpose.
This tool traces and deletes unnecessary files from an image execution, however
the removal of a packages file is not reflected in the installation status of
the package manger.
Therefore, after minimization, the same amount of vulnerabilities is still
reported since image scanners report vulnerabilities according to the installed
packages.
In order to update the package manager information, it is essential to
determine which packages are required for the pipeline to function properly}.
To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, an open-source tool that
helps scientists to make their research reproducible. This tool traces operating system calls used by the
application during execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree of a particular package.
Effectively all needed packages are kept and remaining unnecessary packages are removed. \change{We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages. In this script, we use two temporary
image containers to install Reprozip, collect its trace,
identify the dependencies of the needed packages and then finally use
a fresh image container to
delete unnecessary packages from the image}.

\subsection{Hybrid Approach}

@@

\change{Our experiments concluded considerable discrepancies in the results obtained by
these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
While comparing scanner results, we exluded two images \texttt{bids/antscorticalthickness:v2.2.0-1} and
\texttt{bids/afni\_proc:latest} because Vuls
cannot scan these image, hence no results are present to compare.
%The reason behind excluding
%vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
%to report pending patches that need to be applied to specific packages,
%whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
%vulnerabilities in packages. We exluded other two images because Vuls
%can not scan these image, hence no results are present to compare.
In most cases,
Anchore reports more vulnerabilities than Vuls and Clair resulting in 
the Jaccard coefficient of 0.63 with Clair, 0.59 with Vuls,
whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.86.
Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners in Docker images and the overlap between them.
This Figure also excludes two non-comparable images, which cannot be scanned with Vuls.
It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 699 by Clair, and 536 by Vuls.}
\newline\\
As the number and type of vulnerabilities reported by the these scanners are significantly different from each other,
we desire to investigate the reasons behind these differences.
Following our investigation, we are able to explain some of the reasons behind
the differences. 
Such reasons were resulted from the way these scanners function or behave 
in particular, the following actions by the scanners are indicative:
\begin{itemize}
   \item scanners ignoring vulnerabilities in Linux-kernel-header packages,
   \item scanners referring to different vulnerability databases,
   \item different frequency of updating their databases,
   \item bugs in scanners. 
\end{itemize}

@@

Our second approach involves the deletion of unnecessary packages from the images.
We tested our approach on 5 different images covering the spectrum of Figure~\ref{fig:graph1}.
We find that the image reduction process brings inconsistent deviation in scanning results.
%We find that
%after the size reduction process, sometimes the scanning results deviate only a little from the results
%without minimization. While the minimization process results in significant reduction
%in the number of vulnerabilities in some cases, we find that in other cases the effect
%is negligible. 
In other words, the image reduction was inconsistent.
According to our analysis, this can be due to two reasons: \rom{1}) the number of
deleted packages
and \rom{2}) the kind of deleted packages. 
For an instance, if the deletion is for a package that includes a lot of vulnerabilities,
that particular deletion naturally results in the drop of number of vulnerabilities.
In other
words, deleting more packages reduces more vulnerabilities. 
For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images respectively. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.
